Phenology and Mycorrhizae Manuscript

### 2023-02-01 manuscriptCode_phenologyAndMycorrhizae.Rmd

# funType=mean
# funName="mean"
# calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)
# 
# funType=min
# funName="min"
# calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)
# 
# funType=max
# funName="max"
# calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)

@@

downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)
# combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
#                 inFileName=inFileName,dataPath=dataPath)
# funType=mean
# funName="mean"
# calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)
# 
# funType=min
# funName="min"
# calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)
# 
# funType=max
# funName="max"
# calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)

>>>>

@@

downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)
combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
                inFileName=inFileName,dataPath=dataPath)
# funType=mean
# funName="mean"
# calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)
# 
# funType=min
# funName="min"
# calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)
# 
# funType=max
# funName="max"
# calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funType,funName=funName)
